---
title: "Cartoons"
order: 40
---

## Intro

Analyzing the cartoon dataset

```{r}
#| label: setup
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(mosaic)
library(skimr)
library(crosstable)
library(ggformula)
library(supernova)
```

## Read Data

```{r}
cartoon <- readxl::read_xlsx("../../data/Chhota Bheem vs Doraemon vs Dragon Tales.xlsx")
cartoon
```

## Munging

```{r}
cartoon_modified <- cartoon %>%
  mutate(Gender = as_factor(Gender),
         Cartoob = as_factor(Cartoon))
```

```{r}
cartoon_modified %>% 
  crosstable(Rating ~ Cartoon + Gender) %>% 
  as_flextable()
```

```{r}
cartoon_modified %>% 
  gf_density(~ Rating | Cartoon,
             colour = ~ Cartoon, fill = ~ Cartoon, alpha = 0.3) %>% 
  gf_fitdistr(dist = "norm") %>% 
  gf_refine(theme_classic())

cartoon_modified %>% 
  group_by(Cartoon) %>% 
  summarize (mean_rating = mean(Rating))
             
```

Not really Gaussian? Some look ok!!

## Shapiro Test

```{r}

shapiro.test(cartoon_modified %>% 
               filter(Cartoon == "Chota Bheem") %>% 
               select(Rating) %>%  
               as_vector()) # Can't handle even single col data frame

shapiro.test(cartoon_modified %>% 
               filter(Cartoon == "Doraemon") %>% 
               select(Rating) %>%  
               as_vector()) # Can't handle even single col data frame

shapiro.test(cartoon_modified %>% 
               filter(Cartoon == "Dragon Tales") %>% 
               select(Rating) %>%  
               as_vector()) # Can't handle even single col data frame

```

Chhota Bheem Ratings are normal!! But the others aren't!! India is India!

## Inference

### ANOVA

```{r}
anova_model <- aov(Rating ~ Cartoon, data = cartoon_modified) 

anova_model %>% 
  supernova::supernova()

```

ANOVA says the reduction in error Sum of Squares is merely 6.97! The `p.value` is $0.4028$ so unlikely that the shows are different in mean rating!

```{r}
TukeyHSD(anova_model) %>% broom::tidy()

TukeyHSD(anova_model) %>% 
  broom::tidy() %>% 
  gf_errorbar(conf.low + conf.high ~ contrast, color = ~ contrast, width = 0.2, linewidth = 1) %>% 
  gf_point(estimate ~ contrast) %>% 
  gf_hline(yintercept = 0, linetype = "dashed") %>% 
  gf_theme(theme_classic()) %>% 
  gf_refine(coord_flip())

###

TukeyHSD(anova_model) %>% 
  ggiraphExtra::ggHSD() %>% 
  gf_theme(theme_classic()) %>% 
  gf_theme(theme(axis.text.y = element_text(size = 8, angle = 0)))

```

All confidence intervals straddle 0 so there is no difference in mean score across the Cartoons

### Permutation Test

Just for kicks, a permutation test

```{r}

F_stat <- anova_model %>% 
  supernova::supernova() %>%  pluck(1,6,1) # OK, the F-Statistic
F_stat
##

  
perm_anova_dist <- do(4999) * aov(Rating ~ shuffle(Cartoon), data = cartoon_modified) %>% supernova() %>% pluck(1,6,1)  

head(perm_anova_dist)

gf_histogram(~ result, data = perm_anova_dist) %>% 
  gf_vline(xintercept = ~ F_stat, color = "red") %>% 
  gf_theme(theme_classic())
prop(perm_anova_dist$diffmean <=F_stat)
```

Again the null distribution from permutations staddles the observed mean difference and hence we cannot reject the NULL Hypothesis that there is no difference between Male and Female pocket moneys.
