---
title: "Pocket Money"
order: 20
---

## Intro

Analyzing the pocketmoney dataset

```{r}
#| label: setup
knitr::opts_chunk$set(message = FALSE,warning = FALSE)
library(tidyverse)
library(mosaic)
library(skimr)
library(crosstable)
library(ggformula)
```

## Read Data

```{r}
pocketmoney <- readxl::read_xlsx("../../data/Pocket Money.xlsx")
pocketmoney
```

## Munging

```{r}
pocketmoney_modified <- pocketmoney %>%
  mutate(Gender = as_factor(Gender))
```

```{r}
pocketmoney_modified %>% 
  crosstable(Money_spent ~ Gender) %>% 
  as_flextable()
```

```{r}
pocketmoney_modified %>% 
  gf_density(~ Money_spent | Gender, fill = ~ Gender,
             colour = ~ Gender, alpha = 0.3) %>% 
  gf_fitdistr(dist = "norm") %>% 
  gf_refine(theme_classic())

obs_mean_diff = diffmean(Money_spent ~ Gender, data = pocketmoney_modified)
obs_mean_diff
```

Not really Gaussian.

## Shapiro Test

```{r}

shapiro.test(pocketmoney_modified %>% 
               filter(Gender == "Male") %>% 
               select(Money_spent) %>%  
               as_vector()) # Can't handle even single col data frame

shapiro.test(pocketmoney_modified %>% 
               filter(Gender == "Male") %>% 
               select(Money_spent) %>%  
               as_vector()) # Can't handle even single col data frame
```

Neither of the `Money_spent` sub-variables are normal. So `t-test` won't really work, but still.

## Inference

### t-test

```{r}
mosaic::t_test(Money_spent ~ Gender, data = pocketmoney_modified) %>% 
  broom::tidy()

mosaic::t_test(Money_spent ~ Gender, data = pocketmoney_modified) %>% 
  broom::tidy() %>% 
  gf_errorbar(conf.low + conf.high ~ "Gender", data = ., width = 0.1) %>% 
  gf_point(estimate ~ "Gender") %>% 
  gf_hline(yintercept = 0, linetype = "dashed") %>% 
  gf_refine(coord_flip()) %>% 
  gf_theme(theme_classic())
```

### Wilcoxon Test

```{r}
wilcox.test(Money_spent ~ Gender, data = pocketmoney_modified) %>% 
  broom::tidy()


```

`p.value` in both cases is way to high for us to reject the NULL Hypothesis that there is no difference between Veggies and Non-Veggies in their tip size.

### Permutation Test

Just for kicks, a permutation test

```{r}
null_dist <- do(999) * diffmean(Money_spent ~ shuffle(Gender), data =pocketmoney_modified)
head(null_dist)

gf_histogram(~ diffmean, data = null_dist) %>% 
  gf_vline(xintercept = ~ obs_mean_diff, color = "red") %>% 
  gf_theme(theme_classic())
prop(null_dist$diffmean <= obs_mean_diff)

```

Again the null distribution from permutations staddles the observed mean difference and hence we cannot reject the NULL Hypothesis that there is no difference between Male and Female pocket moneys.
